Using Machine Learning and Constraint Programming to Solve the Relational-To-Ontology Mapping Problem

### 2017-08-10 stp/paper_aaai/main.tex
typo
fig

\usepackage{tikz}
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes.symbols}
\usetikzlibrary{arrows,shapes,decorations.pathmorphing}
\usetikzlibrary{positioning}
\usetikzlibrary{decorations.text}
\usetikzlibrary{decorations.pathmorphing}
\tikzstyle{class}=[draw,ellipse,align=center,fill=green!25]
\tikzstyle{data}=[draw,rectangle,align=center,black!70]
\tikzstyle{hasaA} = [>=stealth',draw,dashed,-,black!70]
\tikzstyle{hasaC} = [>=stealth',draw,thick,-, black]
\tikzstyle{isa} = [>=latex,draw,double,black!90,double distance=1mm]

\newcommand{\authornote}[3]{
  {\fbox{\sc 
  #1}:$\blacktriangleright$\textcolor{#2}{\small{#3}}$\blacktriangleleft$}%
}
\newcommand{\pds}[1]{\authornote{PDS}{purple}{#1}}
\newcommand{\pjs}[1]{\authornote{PJS}{red}{#1}}
\newcommand{\gkg}[1]{\authornote{GKG}{brown}{#1}}
\newcommand{\ddg}[1]{\authornote{DDG}{blue}{#1}}
\newcommand{\npd}[1]{\authornote{NPD}{orange}{#1}}

@@

	\path[draw,hasaA,->] (pe) edge [bend left = 10] 
	node [midway, above, sloped] {name} (-0.5,2);
	\path[draw,hasaA,->] (pe) edge [bend left = 0] 
	node [midway, below, sloped] {birthDate} (0,2);

	\path[draw,hasaA,->] (co) edge [bend left = 0] 
	node [midway, below, sloped] {name} (-1,-5);
	\path[draw,hasaA,->] (co) edge [bend left = 0] 
	node [midway, above, sloped] {phone} (0,-5);
	\path[draw,hasaA,->] (co) edge [bend left = 0] 
	node [midway, above, sloped] {email} (1,-5);

	\path[draw,hasaA,->] (ev) edge [bend left = 0] 
	node [midway, below, sloped] {startDate} (2.5,3.2);
	\path[draw,hasaA,->] (ev) edge [bend left = 0] 
	node [midway, above, sloped] {endDate} (3.5,3.2);
	\path[draw,hasaA,->] (ev) edge [bend left = 0] 
	node [midway, below, sloped] {title} (4.5,3.2);

	\path[draw,hasaA,->] (pl) edge [bend left = 0] 
	node [midway, above, sloped] {name} (6.5,-1.8);
	\path[draw,hasaA,->] (pl) edge [bend left = 0] 
	node [midway, above, sloped] {postalCode} (6,-3);

\end{tikzpicture}
\caption{Example of ontology
(`\tikz{ \node[class] () at (0,0)  {};}' are Classes, `\tikz{ \path[hasaC,->] 
(0,1) -- (3ex,1);}' means ``has a Class property'', 
`\tikz{ \path[hasaA,->] (0,1) -- (3ex,1);}' means ``has a data property'' and 
`\tikz{ \path[isa,->] (0,1) -- (3ex,1);}' means ``is a'' ).
}
\label{FIG:onto}
\end{figure}

>>>>

\usepackage{tikz}
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes.symbols}
\usetikzlibrary{arrows,shapes,decorations.pathmorphing}
\usetikzlibrary{positioning}
\usetikzlibrary{decorations.text}
\usetikzlibrary{decorations.pathmorphing}
\tikzstyle{class}=[draw,ellipse,align=center,fill=green!25]
\tikzstyle{data}=[draw,rectangle,align=center,black!70]
\tikzstyle{hasaA} = 
[>=o,draw,densely dashed,-,black!70,decoration={snake,segment 
length=10,amplitude=1.5,post length=4}]
\tikzstyle{hasaC} = [>=stealth',draw,thick,-, black]
\tikzstyle{isa} = [>=latex,draw,double,black!90,double distance=1mm]

\newcommand{\authornote}[3]{
  {\fbox{\sc 
  #1}:$\blacktriangleright$\textcolor{#2}{\small{#3}}$\blacktriangleleft$}%
}
\newcommand{\pds}[1]{\authornote{PDS}{purple}{#1}}
\newcommand{\pjs}[1]{\authornote{PJS}{red}{#1}}
\newcommand{\gkg}[1]{\authornote{GKG}{brown}{#1}}
\newcommand{\ddg}[1]{\authornote{DDG}{blue}{#1}}
\newcommand{\npr}[1]{\authornote{NPR}{orange}{#1}}

@@

	\path[draw,hasaA,->] (pe) edge [decorate,bend left = 10] 
	node [midway, above, sloped] {name} (-0.5,2);
	\path[draw,hasaA,->] (pe) edge [decorate,bend left = 0] 
	node [midway, below, sloped] {birthDate} (0,2);

	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
	node [midway, below, sloped] {name} (-1,-5);
	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {phone} (0,-5);
	\path[draw,hasaA,->] (co) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {email} (1,-5);

	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
	node [midway, below, sloped] {startDate} (2.5,3.2);
	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {endDate} (3.5,3.2);
	\path[draw,hasaA,->] (ev) edge [decorate,bend left = 0] 
	node [midway, below, sloped] {title} (4.5,3.2);

	\path[draw,hasaA,->] (pl) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {name} (6.5,-1.8);
	\path[draw,hasaA,->] (pl) edge [decorate,bend left = 0] 
	node [midway, above, sloped] {postalCode} (6,-3);

\end{tikzpicture}
\caption{Example of ontology
(`\tikz{ \node[class] () at (0,0)  {};}' are Classes, `\tikz{ \path[hasaC,->] 
(0,1) -- (3ex,1);}' means ``has a Class property'', 
`\tikz{ \path[hasaA] (0,1) edge[decorate] (3ex,1);}' means ``has a data 
property'' and 
`\tikz{ \path[isa,->] (0,1) -- (3ex,1);}' means ``is a'' ).
}
\label{FIG:onto}
\end{figure}
